---
title: "Community context mediates effects of pollinator loss on seed production"
author: "K. C. Arrowsmith, V. A. Reynolds, H. M Briggs, and B. J. Brosi"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true
    code_folding: hide
    theme: cosmo
---

```{r setup - initial, include = F}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Overview
This document contains all code necessary to replicate the analyses for the above article. Any questions about this project can be directed to Kaysee Arrowsmith at kcarrows@uw.edu. 

## Particulars
The data for this analysis come from an experimental bumble bee removal experiment that took place over three years (2011, 2013, and 2014; in 2012, there was a severe drought and we were not able to conduct the experiment) across 14 replicates. Each site had two experimental states (control and manipulation). At each site, we selected focal *Delphinium barbeyi* individuals that were identified with ID numbers (`delph.plant.num`). We further selected specific flowers on that focal individual (`delph.flower.num`) for which we collected and counted seeds. *D. barbeyi* flowers typically produce three carpels, so each selected *D. barbeyi* flower may appear in the dataset up to three times, with each row presenting a separate count of viable seeds produced by that carpel. For each site/state combination, we conducted a pollinator survey, which is summarized in this dataset with *Bombus* richness (`bombus.rich`), abundance (`bombus.abund`, scaled to `bomabund.scale`), and mean fidelity (`mean.fidelity`). The identities of these bees were also considered to determine the relative abundance of long-tongued bees (`prop.long`). For manipulation surveys only, we noted the species of *Bombus* removed (`species.removed`, always the most abundant species from that day's survey) and the number and relative abundance of that species (`num.removed`, `prop.removed`). Once per site (during the control period), we performed a floral survey in which is summarized in these data with the relative abundance of *D. barbeyi* (`prop.delph`) and the similarity between the rest of the floral community and *D. barbeyi* on the morphological axes of color (`color.sim`) and corolla length (`corolla.sim`).

# Load Packages, Functions, Data
```{r setup - packages}
library(tidyverse)
library(kableExtra)
library(broom.mixed)
library(glmmTMB)
library(MuMIn)
library(xtable)
library(DHARMa)
library(performance)
```

```{r setup - functions}
# Function to test for overdispersion (credit Ben Bolker)
overdisp_fun <- function(model) {
    rdf <- df.residual(model)
    rp <- residuals(model,type="pearson")
    Pearson.chisq <- sum(rp^2)
    prat <- Pearson.chisq/rdf
    pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
    c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}


# Function to calculate confidence intervals
## https://stackoverflow.com/questions/48612153/how-to-calculate-confidence-intervals-for-a-vector
confidence_interval <- function(vector, interval) {
  # Standard deviation of sample
  vec_sd <- sd(vector)
  # Sample size
  n <- length(vector)
  # Mean of sample
  vec_mean <- mean(vector)
  # Error according to t distribution
  error <- qt((interval + 1)/2, df = n - 1) * vec_sd / sqrt(n)
  # Confidence interval as a vector
  result <- c("lower" = vec_mean - error, "upper" = vec_mean + error)
  return(result)
}
```

```{r setup - data}
# Clean data
dat <- read.csv("RMBLseeds-cleaned.csv", stringsAsFactors = T)
```

# Check Model Assumptions

We start with a global model using a Poisson distribution.

```{r assumptions - global model}
global.mod <- glmmTMB(viable ~ 
                        prop.removed +
                        bomabund.scale +
                        prop.long + 
                        mean.fidelity + 
                        prop.delph + 
                        color.sim +
                        corolla.sim + 
                        state:bomabund.scale +
                        state:prop.long +
                        state:mean.fidelity +
                        (1|site/delph.plant.num/delph.flower.num) + 
                        (1|year), 
                      data = dat, 
                      family = poisson)
```

## Overdispersion

We use a [function from Ben Bolker](https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#overdispersion) to test for overdispersion in our model. 

```{r assumptions - overdispersion}
# Test for overdispersion
overdisp_fun(global.mod)
```

Significant overdispersion detected (p << 0.05). To account for overdispersion, we switch from a Poisson distribution to a negative binomial.

```{r assumptions - nbinom}
nbinom.mod <- glmmTMB(viable ~ 
                        prop.removed +
                        bomabund.scale +
                        prop.long + 
                        mean.fidelity + 
                        prop.delph + 
                        color.sim +
                        corolla.sim + 
                        state:bomabund.scale +
                        state:prop.long +
                        state:mean.fidelity +
                        (1|site/delph.plant.num/delph.flower.num) + 
                        (1|year), 
                      data = dat, 
                      family = nbinom2)

# Zero-inflated model
nbinom.zi <- glmmTMB(viable ~
                        prop.removed +
                        bomabund.scale +
                        prop.long +
                        mean.fidelity +
                        prop.delph +
                        color.sim +
                        corolla.sim +
                        state:bomabund.scale +
                        state:prop.long +
                        state:mean.fidelity +
                        (1|site/delph.plant.num/delph.flower.num) +
                        (1|year),
                      data = dat,
                      family = nbinom2,
                     zi = ~.)
```

## Zero-inflation

To test for zero-inflation in our data, we use two different methods. First, we perform a chi-squared test to see if there are more zeros than expected. Then, we use an ANOVA to compare global models with and without controlling for zero-inflation.

```{r assumptions - zero-inflation}
# Chi-square test for zero-inflation
contingency <- dat %>%
  mutate(value.cut = cut(viable, breaks = c(-1, 0, 50), labels = c("0", ">0"))) %>%
  with(table(value.cut, state, useNA = "ifany"))
chisq.test(contingency, simulate.p.value = T)

# Likelihood Ratio
anova(nbinom.mod, nbinom.zi)
```

Chi-squared test is marginally significant (p ~ 0.05). AIC is lower for zero-inflated model, and ANOVA is statistically significant (p <<< 0.05). All of this tells us that our data are likely to be zero-inflated and we will therefore use a zero-inflated GLMM.

## Collinearity

Next, we check for collinearity between these variables to ensure that they can all be used in model selection without problems.

```{r assumptions - VIFs}
check_collinearity(nbinom.zi)
# check_collinearity(no.int)
```

We see moderate to high correlation between all of the variables involving the manipulation (`prop.removed` and all interaction terms), which is expected. Importantly, we see low correlation with all of the additive variables that do not involve the strength of the manipulation.


# Model Selection

We use a model selection approach to determine which fixed effects are most important in predicting the number of viable seeds produced by *D. barbeyi*. Because the data was found to be overdispersed, we use the `glmmTMB` package with `family = nbinom2`.

```{r selection, cache = T}
# Creating all combinations of fixed effects and pasting them into a formula
vars <- c("viable",
          "prop.removed",
          "bomabund.scale",
          "prop.delph",
          "prop.long",
          "color.sim",
          "corolla.sim",
          "mean.fidelity",
          "state:bomabund.scale",
          "state:prop.long",
          "state:mean.fidelity"
          )
N <- as.list(seq(1:(length(vars)-1)))
COMB <- sapply(N, function(m) combn(x=vars[2:length(vars)], m))
COMB2 <- list()
k=0
for(i in seq(COMB)){
    tmp <- COMB[[i]]
    for(j in seq(ncol(tmp))){
        k <- k + 1
        COMB2[[k]] <- formula(paste(
          "viable", 
          "~",
          paste(tmp[,j], collapse=" + "), 
          "+ (1|site/delph.plant.num/delph.flower.num) + (1|year)"))
    }
}

# Running glmmTMB for each formula and using glance to isolate AIC values
res <- vector(mode = "list", length(COMB2))
suppressWarnings(for(i in seq(COMB2)){
    res[[i]] <- glance(glmmTMB(COMB2[[i]], data=dat, family = nbinom2, zi = ~.))
})

# Add Model ID column to each tibble
ID <- c(1:length(res))
res2 <- mapply(cbind, res, "Model" = ID, SIMPLIFY = F)

# Removing models that failed to converge)
filt <- Filter(function(x) length(x) > 4, res2) 

# Extracting AIC
filt.df <- data.frame(matrix(unlist(filt), nrow = length(filt), byrow = T))
filt.df[,c('X1', 'X2', 'X4', 'X5')] <- list(NULL)
names(filt.df)[names(filt.df) == 'X3'] <- 'AIC'
names(filt.df)[names(filt.df) == 'X6'] <- 'Model'

# Arranging AICs in increasing order
filt.df <- arrange(filt.df, AIC)
filt.df$delta <- filt.df$AIC - filt.df[1,1]

# Filter out only model outputs with delta < 2
filt.2 <- filt.df[filt.df$delta < 2,]

# Taking the Model IDs from the "best" models (delta < 2) and connecting them with the actual formulas
forms <- data.frame(matrix(unlist(COMB2), nrow = length(COMB2), byrow = T))
colnames(forms) <- "Formula"

forms$Model <- c(1:length(res))
forms$Model <- as.numeric(forms$Model)

mods <- merge(filt.2, forms, by = "Model")
mods <- arrange(mods, AIC)
mods$Formula <- as.character(mods$Formula)

mods %>%
  kable %>%
  kable_styling("striped", full_width = T)
```

# Model Averaging

Because we do not have an obvious "best" model after model selection, we average the top four models ($\Delta AIC < 10^{-7}$).

```{r averaging, cache = T}
# Run all of the models that the model selection spit out
## Create a list with all of the model estimates extracted using tidy
## Filter only the zero-inflated estimates
top.mods <- vector(mode = "list", length(mods$Formula))
for(i in seq(mods$Formula)){
    top.mods[[i]] <- 
      tidy(glmmTMB(as.formula(mods$Formula[[i]]), data=dat, family = nbinom2, zi = ~.)) %>%
      filter(component == "zi") %>%
      mutate(var = ifelse(term == "sd__(Intercept)", group, term)) %>%
      select(var, estimate) %>%
      pivot_wider(names_from = var, values_from = estimate)
}

# Turn the list of estimates for each model into a single dataframe
modselect.results <- data.frame()
temp.df <- data.frame()
for(i in seq(top.mods)){
  temp.df <- as.data.frame(unlist(top.mods[[i]]))
  colnames(temp.df) <- "estimate"
  temp.df$var <- rownames(temp.df)
  temp.wide <- pivot_wider(temp.df, names_from = var, values_from = estimate)
  modselect.results <- bind_rows(modselect.results, temp.wide)
}

# Add model number to this dataframe because otherwise these are all useless
modselect.results$Model <- mods$Model

# Reorganize this table and change variable naming convention
modselect.table <- modselect.results %>%
  dplyr::select(Model, 
         `(Intercept)`,
         prop.removed,
         bomabund.scale,
         prop.long,
         mean.fidelity,
         prop.delph,
         color.sim,
         corolla.sim,
         `statecontrol:bomabund.scale`,
         `statemanipulation:bomabund.scale`,
         `bomabund.scale:statemanipulation`,
         `statecontrol:prop.long`,
         `statemanipulation:prop.long`,
         `prop.long:statemanipulation`,
         `statecontrol:mean.fidelity`,
         `statemanipulation:mean.fidelity`,
         `mean.fidelity:statemanipulation`,
         `delph.flower.num:delph.plant.num:site`,
         `delph.plant.num:site`,
         site,
         year) %>%
  mutate(`state:bomabund.scale` =
           ifelse(!is.na(`statemanipulation:bomabund.scale`) |
                    !is.na(`bomabund.scale:statemanipulation`), "+", ""), 
         `state:prop.long` =
           ifelse(!is.na(`statemanipulation:prop.long`) |
                  !is.na(`prop.long:statemanipulation`), "+", ""),
         `state:mean.fidelity` =
           ifelse(!is.na(`statemanipulation:mean.fidelity`) |
                    !is.na(`mean.fidelity:statemanipulation`), "+", "")) %>%
  dplyr::select(Model, 
         `(Intercept)`,
         prop.removed,
         bomabund.scale,
         prop.long,
         mean.fidelity,
         prop.delph,
         color.sim,
         corolla.sim, 
         `state:bomabund.scale`, 
         `state:prop.long`, 
         `state:mean.fidelity`, 
         `delph.flower.num:delph.plant.num:site`, 
         `delph.plant.num:site`, 
         site, 
         year)

# Filter top models
tiptop <- mods %>%
  filter(delta < 10^-6)

form.list <- as.list(rep(NA, times = nrow(tiptop)))
for(i in 1:nrow(tiptop)) {
  form.list[[i]] = glmmTMB(as.formula(tiptop$Formula[i]), data = dat, family = poisson, zi = ~.)
}

# Model average
top.avg <- model.avg(form.list)

avg.table <- as.data.frame(summary(top.avg)[9]) %>%
  rownames_to_column(var = "variable") %>%
  filter(str_detect(variable, "zi")) %>%
  column_to_rownames(var = "variable")
avg.table %>%
  kable %>%
  kable_styling("striped", full_width = T)
```

# Effect of Abundance

We test whether our manipulation has a significant impact on *Bombus* abundance that could affect interpretation of results.

```{r abundance}
abund.test <- glmmTMB(bombus.abund ~ state + (1|site/delph.plant.num/delph.flower.num) + (1|year), data = dat, family = poisson)
summary(abund.test)
```

The manipulation does not have a statistically significant effect on *Bombus* abundance (p = 0.917).


# Visits to D. barbeyi

We explore how our manipulation influenced the relative abundance of pollinator visits to *D. barbeyi* compared to other flowers.

```{r dbarb visits, warning = F, message = F}
dat.site <- dat %>%
  group_by(site, state, year) %>%
  summarise(prop.removed = unique(prop.removed),
            bombus.abund = unique(bombus.abund),
            prop.long = unique(prop.long))

forage <- read.csv("../Data/forage-cleaned.csv", stringsAsFactors = F)
delph.dat <- read.csv("../Data/dbarbcounts.csv", stringsAsFactors = F)

forage2 <- forage %>%
  mutate(plant.simple = ifelse(plant.species == "Delphinium barbeyi", "Dbarb", "NotDbarb"),
         year = as.numeric(year)) %>%
  group_by(site, state, year, plant.simple) %>%
  summarise(total.visits = sum(num.indiv.visited)) %>%
  pivot_wider(names_from = "plant.simple",
              values_from = "total.visits") %>%
  left_join(dat.site, by = c("site", "state", "year")) %>%
  left_join(delph.dat, by = "site") %>%
    mutate(prop.dbvisit = Dbarb/(Dbarb + NotDbarb))

dbvisit.test <- glmmTMB(cbind(Dbarb, NotDbarb) ~
                          prop.removed + 
                          bombus.abund +
                          prop.long +
                          num.delph +
                          prop.delph +
                          state:bombus.abund +
                          state:prop.long + 
                          (1|site) +
                          (1|year),
                        data = forage2,
                        family = binomial)
summary(dbvisit.test)
```

We find that our manipulation interacted with *Bombus* abundance and distribution of tongue lengths to significantly influence the proportion of *Bombus* foraging visits to *D. barbeyi*.

# Figures

Code to produce all figures included in the manuscript.

## Model Prediction

Generate model predictions so that our plots will show the trends found in our model selection and averaging. 

```{r pred}
pred.dat <- expand.grid(
    prop.removed = seq(from = min(dat$prop.removed, na.rm = T), to = max(dat$prop.removed, na.rm = T), length.out = 4),
    bomabund.scale = seq(from = min(dat$bomabund.scale), to = max(dat$bomabund.scale), length.out = 4),
    viable = 0,
    state = c("control", "manipulation"),
    prop.delph = seq(from = min(dat$prop.delph), to = max(dat$prop.delph), length.out = 4),
    prop.long = seq(from = min(dat$prop.long), to = max(dat$prop.long), length.out = 4),
    mean.fidelity = seq(from = min(dat$mean.fidelity, na.rm = T), to = max(dat$mean.fidelity, na.rm = T), length.out = 4),
    color.sim = seq(from = min(dat$color.sim), to = max(dat$color.sim), length.out = 4),
    corolla.sim = seq(from = min(dat$corolla.sim), to = max(dat$corolla.sim), length.out = 4),
    site = c("site1", "site2"),
    delph.plant.num = rep(1:2),
    delph.flower.num = rep(1:2),
    year = c("year1", "year2")
)

# type = zlink should call the zero-inflated results
pred.dat$viable <- predict(top.avg, pred.dat, type =  "zlink", full = T, allow.new.levels = T)
```

## Figure 1

```{r Fig1, warning = F, message = F}
## Data for geom_pointrange
dat.manip <- dat[dat$state == "manipulation",]
manip.sum <- dat.manip %>%
  group_by(site, year, prop.removed, bombus.abund, mean.fidelity) %>%
  summarise(mean.viable = mean(viable, na.rm = T),
            lower.ci = confidence_interval(na.omit(viable), 0.95)[[1]],
            higher.ci = confidence_interval(na.omit(viable), 0.95)[[2]])

## Data for geom_smooth
pred.manip <- pred.dat %>%
  filter(prop.removed > 0)

proprem.plot <- ggplot() +
  geom_pointrange(data = manip.sum, 
                  aes(x = prop.removed,
                      y = mean.viable,
                      ymin = lower.ci,
                      ymax = higher.ci),
                  size = 1,
                  shape = 17,
                  color = "grey") +
  geom_smooth(data = pred.manip, 
              aes(x = prop.removed, 
                  y = as.integer(exp(viable))), 
              method = "glm",
              method.args = list(family = poisson(link = "log")),
              col = "black",
              linetype = "dashed",
              se = F) +
  theme_classic(base_size = 22) +
  labs(x = "Proportion of "~italic(Bombus)~" Community Removed",
       y = "Viable Seeds") +
  coord_cartesian(xlim = c(0.5, 1))
proprem.plot
```

## Figure 2

```{r Fig2}
## Data for geom_pointrange
trait.sum <- dat %>%
  group_by(site, color.sim, corolla.sim, year) %>%
  summarise(mean.viable = mean(viable, na.rm = T),
            lower.ci = confidence_interval(na.omit(viable), 0.95)[[1]],
            higher.ci = confidence_interval(na.omit(viable), 0.95)[[2]])

color.plot <- ggplot() +
  geom_pointrange(data = trait.sum, aes(x = color.sim, 
                                    y = mean.viable, 
                                    ymax = higher.ci, 
                                    ymin = lower.ci),
                  size = 1,
                  col = "grey") +
  geom_smooth(data = pred.dat, 
              aes(x = color.sim, y = as.integer(exp(viable))), 
              method = "glm",
              method.args = list(family = poisson(link = "log")),
              col = "black",
              linetype = "dashed",
              se = F) +
  theme_classic(base_size = 22) +
  labs(x = "Blue Flowers",
       y = "Viable Seeds")
color.plot

corolla.plot <- ggplot() +
  geom_pointrange(data = trait.sum, aes(x = corolla.sim, 
                                    y = mean.viable, 
                                    ymax = higher.ci, 
                                    ymin = lower.ci),
                  size = 1,
                  col = "grey") +
  geom_smooth(data = pred.dat, 
              aes(x = corolla.sim, y = as.integer(exp(viable))), 
              method = "glm",
              method.args = list(family = poisson(link = "log")),
              col = "black",
              linetype = "dashed",
              se = F) +
  theme_classic(base_size = 22) +
  labs(x = "Corolla Length 10 - 18mm",
       y = "Viable Seeds")
corolla.plot
```

## Figure 3

```{r state-abund}
# to unscale bomabund.scale, multiply by scaling factor and then add center
# look at str(dat) to find that
# scale = 70.5, center = 3
pred.dat <- pred.dat %>%
  mutate(bombus.abund = (bomabund.scale * 70.5) + 3)

# Data for geom_pointrange
dat.sum <- dat %>%
  group_by(site, state, bombus.abund, prop.long) %>%
  summarise(mean.viable = mean(viable, na.rm = T),
            lower.ci = confidence_interval(na.omit(viable), 0.95)[[1]],
            higher.ci = confidence_interval(na.omit(viable), 0.95)[[2]])

state.abund <- ggplot() +
  geom_pointrange(data = dat.sum, aes(x = bombus.abund, 
                                    y = mean.viable, 
                                    ymax = higher.ci, 
                                    ymin = lower.ci,
                                    shape = state),
                  size = 1,
                  color = "grey") +
  geom_smooth(data = pred.dat,
              aes(x = bombus.abund,
                  y = as.integer(exp(viable)),
                  linetype = state),
              method = "glm",
              method.args = list(family = poisson(link = "log")),
              col = "black",
              se = F) +
  labs(x = ~italic(Bombus)~" Abundance",
       y = "Viable Seeds",
       shape = "State",
       linetype = "State") +
  theme_classic(base_size = 22)
state.abund
```

## Figure 4

```{r state-tongue}
state.tongue <- ggplot() +
  geom_pointrange(data = dat.sum, aes(x = prop.long, 
                                    y = mean.viable, 
                                    ymax = higher.ci, 
                                    ymin = lower.ci,
                                    shape = state),
                  size = 1,
                  color = "grey") +
  geom_smooth(data = pred.dat,
              aes(x = prop.long,
                  y = as.integer(exp(viable)),
                  linetype = state),
              method = "glm",
              method.args = list(family = poisson(link = "log")),
              col = "black",
              se = F) +
  labs(x = "Relative Abundance of Long-Tongued Bees",
       y = "Viable Seeds",
       shape = "State",
       linetype = "State") +
  theme_classic(base_size = 22)
state.tongue
```

## Figure 5

```{r db visits}
propdbtongue.plot <- ggplot(forage2, aes(x = prop.long, 
                                         y = prop.dbvisit, 
                                         shape = state, 
                                         linetype = state)) +
  geom_point(size = 1,
             color = "grey") +
  geom_smooth(method = "glm", 
              method.args = list(family = binomial()),
              col = "black",
              se = F) +
  coord_cartesian(ylim = c(0, 1)) +
  labs(x = "Relative Abundance of Long-Tongued Bees",
       y = "Proportion of "~italic(Bombus)~"Visits",
       shape = "State",
       linetype = "State") +
  theme_classic(base_size = 22)
propdbtongue.plot

propdbabund.plot2 <- ggplot(forage2, aes(x = bombus.abund, 
                                         y = prop.dbvisit, 
                                         shape = state, 
                                         linetype = state)) +
  geom_point(size = 1,
             color = "grey") +
  geom_smooth(method = "glm", 
              method.args = list(family = binomial()),
              col = "black",
              se = F) +
  coord_cartesian(ylim = c(0, 1)) +
  labs(x = ~italic(Bombus)~" Abundance",
       y = "Proportion of "~italic(Bombus)~"Visits",
       shape = "State",
       linetype = "State") +
  theme_classic(base_size = 22)
propdbabund.plot2
```


# Session Info

```{r session info}
sessionInfo()
```